### 2023-02-27 output/DiD_crime/tables/balance_table.tex
Abstracted DiD code

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & Zestimate, Jan. 2017 & 291,945.81 & 26,673.96 & 0.00 & 3,189.17 & 0.75 \\
 & Change, Jan. 2017 to Jan. 2019 & 50,501.64 & 2,697.85 & 0.27 & -3,196.88 & 0.32 \\
\cline{1-7}
\multirow[c]{7}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.25 & 0.01 & 0.09 & -0.00 & 0.96 \\
 & Jobs per square mile (2010) & 4,161.51 & 259.78 & 0.64 & 668.27 & 0.37 \\
 & Median household income (2016) & 52,084.78 & 2,271.04 & 0.03 & -211.14 & 0.87 \\
 & Population density (2010) & 9,018.27 & 962.56 & 0.01 & 644.23 & 0.17 \\
 & Median two bedroom rent (2015) & 1,093.52 & 33.19 & 0.05 & 8.19 & 0.69 \\
 & Share white (2010) & 0.60 & 0.03 & 0.00 & -0.00 & 0.94 \\
 & Share with commute $<$15 minutes (2010) & 0.29 & -0.01 & 0.02 & -0.01 & 0.29 \\
\cline{1-7}
\textit{Panel C} & For cause & 0.12 & 0.01 & 0.67 & -0.01 & 0.56 \\
\cline{1-7}
\textit{Panel D} & Defendant is an entity & 0.01 & 0.00 & 0.36 & 0.00 & 0.64 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & Crimes reported, Jan. 2017 & 1.51 & 0.35 & 0.57 & 0.14 & 0.82 \\
 & Change in Crimes Reported, Jan. 2017 to Jan. 2019 & -0.02 & 0.07 & 0.50 & 0.05 & 0.65 \\
\cline{1-7}
\textit{Panel B} & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & -0.01 & 0.11 \\
\cline{1-7}
\textit{Panel D} & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.01 & 0.16 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-02-27 output/summary_statistics/tables/summary_statistics.tex
Abstracted DiD code

\begin{tabular}{llcccc}
\toprule
 &  & Mean & S.D. & N \\
Panel & Variable &  &  &  \\
\midrule
\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Zestimates}} & Zestimate, Jan. 2017 & 298,908.73 & 352,754.39 & 10,176 \\
 & Zestimate, Jan. 2019 $-$ Zestimate, Jan. 2017 & 46,593.74 & 158,125.14 & 10,160 \\
\cline{1-5}
\multirow[c]{7}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per sq. mile (2010) & 4,797.07 & 17,579.99 & 40,726 \\
 & Median household income (2016) & 52,659.44 & 27,177.48 & 40,726 \\
 & Population density (2010) & 9,159.77 & 9,574.14 & 40,726 \\
 & Share below poverty line & 0.20 & 0.15 & 40,726 \\
 & Share white (2010) & 0.58 & 0.29 & 40,726 \\
 & Share with bachelor's degree & 0.26 & 0.17 & 40,726 \\
 & Share with commute $<$15 min. (2010) & 0.28 & 0.11 & 40,726 \\
\cline{1-5}
\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.33 & 40,727 \\
 & No cause & 0.11 & 0.31 & 40,727 \\
 & Non-payment of rent & 0.75 & 0.43 & 40,727 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,727 \\
 & Defendant is an entity & 0.01 & 0.08 & 40,727 \\
 & Plaintiff has an attorney & 0.84 & 0.37 & 40,727 \\
 & Plaintiff is an entity & 0.70 & 0.46 & 40,727 \\
\cline{1-5}
\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 40,727 \\
 & Case dismised & 0.29 & 0.45 & 40,727 \\
 & Case duration & 57.81 & 78.29 & 39,087 \\
 & Case heard & 0.06 & 0.23 & 40,727 \\
 & Case mediated & 0.41 & 0.49 & 40,727 \\
 & Money judgment & 1,890.34 & 5,279.49 & 40,727 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel F: Post-treatment Zestimates}} & At filing date & 377,384.02 & 316,645.29 & 10,096 \\
 & One year after filing date & 421,601.75 & 344,328.86 & 10,443 \\
 & Three years after filing date & 501,611.80 & 780,467.01 & 5,894 \\
 & Two years after filing date & 477,948.08 & 457,694.83 & 9,175 \\
\cline{1-5}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcccc}
\toprule
 &  & Mean & Median & S.D. & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{4}{4cm}{\textit{Panel A: Pre-treatment Zestimates}} & Change in Crimes Reported, Jan. 2017 to Jan. 2019 & -0.01 & 0.00 & 0.76 & 40,734 \\
 & Change in Zestimate, Jan. 2017 to Jan. 2019 & 46,593.08 & 37,330.00 & 158,125.24 & 10,160 \\
 & Crimes reported, Jan. 2017 & 0.21 & 0.00 & 4.79 & 40,734 \\
 & Zestimate, Jan. 2017 & 298,898.22 & 235,078.00 & 352,756.46 & 10,176 \\
\cline{1-6}
\multirow[c]{8}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per square mile (2010) & 4,802.71 & 1,355.40 & 17,583.20 & 40,732 \\
 & Median household income (2016) & 52,695.02 & 47,105.00 & 27,212.35 & 40,732 \\
 & Median two bedroom rent (2015) & 1,116.73 & 1,055.00 & 396.69 & 30,546 \\
 & Population density (2010) & 9,151.92 & 5,982.68 & 9,537.28 & 40,732 \\
 & Share below poverty line & 0.20 & 0.16 & 0.15 & 40,732 \\
 & Share white (2010) & 0.58 & 0.63 & 0.29 & 40,732 \\
 & Share with bachelor's degree & 0.26 & 0.22 & 0.17 & 40,732 \\
 & Share with commute $<$15 minutes (2010) & 0.28 & 0.27 & 0.11 & 40,732 \\
\cline{1-6}
\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,734 \\
 & No cause & 0.11 & 0.00 & 0.31 & 40,734 \\
 & Non-payment of rent & 0.75 & 1.00 & 0.43 & 40,734 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,734 \\
 & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,734 \\
 & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,734 \\
 & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,734 \\
\cline{1-6}
\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,734 \\
 & Case dismised & 0.29 & 0.00 & 0.45 & 40,734 \\
 & Case duration & 57.81 & 21.00 & 78.28 & 39,094 \\
 & Case heard & 0.06 & 0.00 & 0.23 & 40,734 \\
 & Case mediated & 0.41 & 0.00 & 0.49 & 40,734 \\
 & Money judgment & 1,890.02 & 0.00 & 5,279.08 & 40,734 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel F: Post-treatment Zestimates}} & Crimes one year after filing date & 0.19 & 0.00 & 4.32 & 40,734 \\
 & Crimes two years after filing date & 0.18 & 0.00 & 4.40 & 35,684 \\
 & Zestimate one year after filing date & 421,590.21 & 347,444.00 & 344,333.24 & 10,443 \\
 & Zestimate two years after filing date & 477,931.84 & 393,800.00 & 457,699.06 & 9,175 \\
\cline{1-6}
\bottomrule
\end{tabular}
